A generic and fast C++ optimization framework

### 2017-10-18 paper.tex
Add simple objective function and policy design pattern.

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{tabularx}
\usepackage{threeparttable}

@@

\usepackage[]{nips_2017}

@@

@@

  \item Simulated Annealing

  \item Frank-Wolfe algorithm

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{listings}

@@

\usepackage[final]{nips_2017}

@@

For instance, the code below defines a simple sparse function, where each
dimension has a parabola with a distinct minimum.

\begin{lstlisting}
class SparseFunction
{
  SparseFunction()
  {
    intercepts = arma::vec("20 12 15 100");
    bi = arma::vec("-4 -2 -3 -8");
  }

  double Evaluate(const arma::mat& p, const size_t i)
  {
    return p[i] * p[i] + bi[i] * p[i] + intercepts[i];
  }

  void Gradient(const arma::mat& p, const size_t i, arma::sp_mat& g)
  {
    g.zeros(arma::size(p));
    g[i] = 2 * p[i] + bi[i];
  }
}

\end{lstlisting}

Another important component of the optimization framework design is flexibility. To this end, we use a C++ programming paradigm known as policy-based design \cite{Alexandrescu2001}. In short, this means that the behavior is easily controllable by the user, simply by specifying template parameters. For example, the SGD class, which is used as basis for other stochastic gradient descent methods, accepts a template parameter UpdateType. Thus, if the user wants to update the learning rate update strategy that mlpack does not have support for, they merely need to implement a optimizer class, and then they can use the type SGD<MyCustomLearningRate>. Additionally, because templates are being used, there is no additional overhead, as there would be when providing this type of support through inheritance or in other languages such as Python or C

@@

  \item {\bf Annealing variants:} Simulated Annealing

  \item {\bf Else:} Conditional Gradient Descent (Frank-Wolfe algorithm)
